\documentclass[dvipsnames,parskip,a4paper]{scrartcl}

% Colour and design packages
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning}

\usepackage{pifont}
\usepackage{graphicx}
\usepackage{etoolbox}
\usepackage{longtable}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.5cm]{geometry}

\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}

% To make sure we don't have page numbers.
\usepackage{nopageno}

% Our consistent sizing
\newcommand{\cardroundingradius}{4mm}
\newcommand{\cardboxroundingradius}{0.5mm}
\newcommand{\cardtextborderspace}{1.4mm}
\newcommand{\cardwidth}{57mm}
\newcommand{\cardheight}{86mm}
\newcommand{\cardimageheight}{43mm}
\newcommand{\cardtitleheight}{7.1mm}
\newcommand{\cardtextheight}{14.3mm}
\newcommand{\cardtcspace}{4mm}
\newcommand{\cardtcheight}{6mm}
\newcommand{\circlesize}{1.25mm}

% Our consistent colours
\newcommand{\cardtitlecolour}{lightgray}
\newcommand{\cardtextboxcolour}{lightgray}
\newcommand{\cardvaluecolour}{lightgray}
\newcommand{\cardtypecolour}{lightgray}

% Our card template
\newcommand{\card}[4]{

\begin{tikzpicture}[baseline = (current bounding box.center)]
\draw[rounded corners = \cardroundingradius] (0,0) rectangle
    (\cardwidth, \cardheight);

\node (title) at (0.5 * \cardwidth, \cardheight - \cardroundingradius)
    [ anchor = north, fill = \cardtitlecolour!20, draw = \cardtitlecolour, thick,
    rounded corners = \cardboxroundingradius,
    text width = \cardwidth - 2 * (\cardroundingradius + \cardtextborderspace),
    minimum height = \cardtitleheight]
    { \Large #1 };

\node (text) at (0.5 * \cardwidth, \cardroundingradius + \cardtcheight + \cardtcspace)
    [ anchor = south, fill = \cardtextboxcolour!20, draw = \cardtextboxcolour, thick,
    rounded corners = \cardboxroundingradius,
    text width = \cardwidth - 2 * (\cardroundingradius + \cardtextborderspace),
    text depth = \cardtextheight, align = justify]
    { #3 };

\node (type)
    [ fill = \cardtypecolour!20, draw = \cardtypecolour, thick,
    below left = \cardtcspace + \cardtcheight and 0mm of text, anchor = south west,
    rounded corners = \cardboxroundingradius,
    minimum height = \cardtcheight]
    { #2 };

\node (cost)
    [ fill = \cardvaluecolour!20, draw = \cardvaluecolour, thick,
    below right = \cardtcspace + \cardtcheight and 0mm of text, anchor = south east,
    rounded corners = \cardboxroundingradius,
    minimum height = \cardtcheight]
    { #4 Gold };

\end{tikzpicture}%

}

% Elemental symbols
\newcommand{\drawcircle}[1]{\tikz[baseline = (current bounding box.south)]\draw[darkgray, fill = #1] (0,0) circle (\circlesize);}}
\newcommand{\fire}{\drawcircle{Red}}
\newcommand{\earth}{\drawcircle{Sepia}}
\newcommand{\water}{\drawcircle{RoyalBlue}}
\newcommand{\nature}{\drawcircle{Green}}
\newcommand{\magic}{\drawcircle{Mulberry}}
\newcommand{\gold}{\drawcircle{Yellow}}
\newcommand{\chance}{\drawcircle{Orange}}

% Costs
\newcommand{\free}{0}
\newcommand{\onecost}{3}
\newcommand{\twocost}{7}
\newcommand{\threecost}{12}
\newcommand{\fourcost}{18}

\title{Rules and Cards for Elemental Deck Builder}
\author{Emil Indzhev}

\begin{document}

\maketitle

\begin{itemize}

\item

The game is played between two players who take turns. The player whose health reaches zero first loses and the other wins.

\item

Seven dice determine the strengths of various cards: fire \fire, earth \earth, water \water, nature \nature, magic \magic, gold \gold \ and chance \chance. The first six are rolled at the start of the game. The seventh one is rolled whenever its value is needed (possibly multiple times per turn).

\item

Players start with 100 health, 6 gold, 5 Basic Income cards in their deck and no cards in their hand. The player whose health reaches 0 first loses. If both players' health pools reach 0 at the same time, the one with more health wins. If equal, the player with more gold wins.

\item

All other cards are shuffled into two decks: cheap (costing \onecost \ or \twocost \ gold) and expensive (costing \threecost \ or \fourcost \ gold). Four cards are dealt from each deck. Those are the shops from which cards can be purchased. At the end of a player's turn, the oldest card in each of the two card shops is removed, if no card was bought from that shop. Then both shops are refilled back to four cards from their respective decks. The removed cards are set aside. When a store's deck is empty but a card must be drawn from it, the pile of removed cards is shuffled and added to the store's deck.

\item

On each turn a player may do the following in any order: gain one gold, draw one card, discard any number of cards, play one action, play any number of blessings and/or bid for one card. When a card is played, its effect is executed and then it goes to the discard pile. When a player must draw but their deck is empty, their discard pile is shuffled and then added to their deck. The player must end their turn with at most 5 cards in their hand.

\item

Playing an action consists of either executing it or placing it face down on the table for a later turn. Executing it later isn't counted towards that turn's action limit but requires paying half its card cost.

\item

A player may respond to their opponent's action by playing an action which affects (or may affect) its result; the response is executed before the action that triggered it. This requires paying half the card cost of the action but does not count towards the player's action limit on their next turn. The action may either come from the player's hand or their face down actions. The opponent is then allowed to play further actions and/or blessings before executing the original action that triggered the response. In the case of actions, the player may respond to them as well.

\item

If a card is played and its effect needs the top $X$ cards of a player's deck, but the deck has fewer than $X$ cards, the player's discard pile is shuffled and added to the bottom of their deck.

\item

Bidding for a card consists of a player announcing their interest in buying a card from one of the shops for its stated cost. Then their opponent may outbid them to two times that. The player may then match their opponent's bid. This bidding in multiples of the stated cost continues until either the opponent doesn't outbid or the player doesn't match. The player is allowed to play actions during the auction. Its winner gets the card. If it is a passive card, it is immediately activated for the rest of the game. Otherwise, it is added to the player's discard pile.

\item

A player dealing damage (to their opponent or themselves) receives gold equal to the damage dealt.

\item

All fractional number amounts are always rounded up before execution.

\end{itemize}

\newpage

\begin{longtable}{ c c c }

\card{Fire}{Action}{Deal \fire \ damage to your opponent.}{\twocost}
&
\card{Tremor}{Action}{Deal \earth \ damage to your opponent.}{\twocost}
&
\card{Heavy Rain}{Action}{Deal \water \ damage to both yourself and  your opponent.}{\twocost}
&
\card{Blind Attack}{Action}{Deal \chance \ to your opponent.}{\twocost}
&
\card{Blazing Fire}{Action}{Deal $2 \times$\fire \ damage to your opponent.}{\threecost}
&
\card{Earthquake}{Action}{Deal $2 \times$\earth \ damage to your opponent.}{\threecost}
&
\card{Rainstorm}{Action}{Deal $2 \times$\water \ damage to both yourself and  your opponent.}{\threecost}
&
\card{Haphazard Offence}{Action}{Deal $2 \times$\chance \ to your opponent.}{\threecost}
&
\card{Magical Firestorm}{Action}{Deal \magic$\times$\fire \ damage to your opponent.}{\fourcost}
&
\card{Meteor Strike}{Action}{Deal \magic$\times$\earth \ damage to your opponent.}{\fourcost}
&
\card{Biblical Flood}{Action}{Deal \magic$\times$\water \ damage to both yourself and your opponent.}{\fourcost}
&
\card{TODO}{Action}{Deal \magic$\times$\chance \ damage to your opponent.}{\fourcost}
&
\card{Volcanic Eruption}{Action}{Deal \fire$\times$\earth \ damage to your opponent.}{\fourcost}
&
\card{TODO} {Action}{Deal \fire$\times$\chance \ damage to your opponent.}{\fourcost}
&

\card{Ecology}{Action}{Heal \nature \ health.}{\onecost}
&
\card{Reforestation}{Action}{Heal $2 \times$\nature \ health.}{\twocost}
&
\card{Nature Reserves}{Action}{Heal \nature$\times$\earth \ health.}{\threecost}
&
\card{Hot Springs}{Action}{Heal \nature$\times$\water \ health.}{\threecost}
&
\card{Mystical Restoration}{Action}{Heal \nature$\times$\magic \ health.}{\threecost}
& 

\card{Marketplace}{Action}{Gain \gold \ gold.}{\onecost}
&
\card{Treasury}{Action}{Gain $2 \times$\gold \ gold.}{\twocost}
&
\card{Gold Mine}{Action}{Gain \gold$\times$\earth \ gold.}{\threecost}
&
\card{Gold Panning}{Action}{Gain \gold$\times$\water \ gold.}{\threecost}
&
\card{Ancient Alchemy}{Action}{Gain \gold$\times$\magic \ gold.}{\threecost}
&
\card{Speculative Investment}{Action}{Gain \gold$\times$\chance \ gold.}{\threecost}
&

\card{Water Reservoirs}{Passive}{Shield \water \ against \fire \ damage.}{\twocost}
&
\card{Solid Infrastructure}{Passive}{Shield \earth \ against \earth \ and \water \ damage.}{\twocost}
&
\card{Natural Forests}{Passive}{Shield \nature \ against \magic \ and \water \ damage.}{\twocost}
&
\card{Paid Militia}{Passive}{Shield any amount of damage by paying one gold to your opponent per unit of damage.}{\threecost}
&
\card{Magical Barrier}{Passive}{Shield \magic$\times$\magic \ against combo damage.}{\fourcost}
&
 
\card{Prometheus's Gift}{Action}{Triple the strength of all your \fire \ effects.}{\threecost}
&
\card{Gaia's Protection}{Action}{Double the strength of all your \earth \ effects.}{\threecost}
&
\card{Poseidon's Trident}{Action}{Double the strength of all your \water \ effects.}{\threecost}
&
\card{Ancient Grimoire}{Action}{Double the strength of all your \magic \ effects.}{\threecost}
&
\card{Nymphs' Grace}{Action}{Double the strength of all your \nature \ effects.}{\twocost}
&
\card{Midas Touch}{Action}{Double the strength of all your \gold \ effects.}{\twocost}
&
\card{Purism}{Action}{Double the strength of all your non-combo effects.}{\twocost}
&

\card{Gambling}{Action}{Reroll a die once.}{\onecost}
&
\card{Cheap Trick}{Action}{Change the value of a die by one.}{\onecost}
&
\card{Second Chance}{Action}{Reroll a die up to twice.}{\twocost}
&
\card{Sleight of Hand}{Action}{Change the value of a die by up to two.}{\twocost}
&
\card{Calculated Risk}{Action}{Reroll a die up to four times.}{\threecost}
&
\card{Smoke and Mirrors}{Action}{Change the value of a die by up to three.}{\threecost}
&
\card{Perspective Shift}{Action}{Flip a die over.}{\threecost}
&
\card{Trickster God}{Action}{Swap the values of two dice.}{\fourcost}
&

\card{Mirror Wall}{Blessing}{Draw a card and look at your opponent's hand.}{\onecost}
&
\card{Mirror Table}{Blessing}{Draw a card and look at your opponent's face down actions.}{\onecost}
&
\card{Sneak Peek}{Blessing}{Draw a card and look at the top 2 cards of your deck.}{\onecost}
&
\card{Reconnaissance}{Blessing}{Draw a card and look at the top 3 cards of your opponent's deck.}{\onecost}
&
\card{Impatience}{Action}{Look at and reorder the top 4 cards of your deck.}{\twocost}
&
\card{Sabotage}{Action}{Look at and reorder the top 5 cards of your opponent's deck.}{\twocost}
&
\card{Magnetic Hands}{Action}{Move a chosen card from your deck to your hand and then shuffle your deck.}{\threecost}
&

\card{Deep Pockets}{Passive}{You may bid for more than card per turn.}{\twocost}
&
\card{Express Shipping}{Passive}{All cards you buy go into your hand.}{\threecost}
&

\card{Weak Hands}{Blessing}{Your opponent must discard 3 cards from their hand.}{\threecost}
&
\card{Faulty Table}{Blessing}{Your opponent must discard 3 cards from their face down actions.}{\threecost}
&
\card{Veto}{Action}{Cancel an action of your opponent.}{\threecost}
&

\card{Multitasking Novice}{Blessing}{Play up to 1 additional action.}{\onecost}
&
\card{Multitasking Master}{Blessing}{Play up to 2 additional actions.}{\twocost}
&
\card{Multitasking Lord}{Blessing}{Play up to 3 additional actions.}{\threecost}
&
\card{Multitasking God}{Blessing}{Play up to 4 additional actions}{\fourcost}
&

\card{Exploration Novice}{Action}{Draw 2 more cards.}{\onecost}
&
\card{Exploration Master}{Action}{Draw 3 more cards.}{\twocost}
&
\card{Exploration Lord}{Action}{Draw 4 more cards.}{\threecost}
&
\card{Exploration God}{Action}{Draw 5 more cards.}{\fourcost}
&

\card{Recycling Novice}{Action}{Remove up to 1 card from your hand and return them to the card store.}{\onecost}
&
\card{Recycling Master}{Action}{Remove up to 2 cards from your hand and return them to the card store.}{\twocost}
&
\card{Recycling Lord}{Action}{Remove up to 3 cards from your hand and return them to the card store.}{\threecost}
&
\card{Recycling God}{Action}{Remove up to 4 cards from your hand and return them to the card store.}{\fourcost}
&

\card{Big Handed}{Passive}{You may now hold 3 additional cards in your hand.}{\twocost}
&
\card{Cheapskate}{Passive}{Face down actions and action responses no longer cost gold to play.}{\threecost}
&
\card{Proactive}{Passive}{You may draw a card as an action.}{\threecost}
&
\card{Truly Blessed}{Passive}{Draw a card the first time you play a blessing.}{\fourcost}
&

\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&
\card{Basic Income}{Blessing}{Gain 1 gold.}{\free}
&

\card{}{ \hspace{15mm} }{}{ \hspace{3mm} }
&
\card{}{ \hspace{15mm} }{}{ \hspace{3mm} }
&
\card{}{ \hspace{15mm} }{}{ \hspace{3mm} }
&

\end{longtable}

\end{document}
